### 2024-10-31 project3/draft.tex
new

\begin{table}[ht!]
    \centering
    \begin{tabular}{lrr}
        \toprule
        \textbf{Model} & \textbf{Training MSE} & \textbf{True MSE} \\
        \midrule
        Without TL & 0.3588 & 0.4188 \\
        Fine Tuning & 0.1690 & 0.1780 \\
        Layer Freezing & 0.1828 & 0.2295 \\
        Extensive Training & 0.0853 & 0.0726 \\
        \bottomrule
    \end{tabular}
    \caption{Comparison of different TL methods on GMWB contracts}
    \label{tab3:transfer_learning_results_gmwb}
\end{table}

Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the LSTM metamodels on the GMWB contracts.
The suboptimal performance of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge significantly.
In such circumstances, fine-tuning provides a better approach by allowing the metamodel to leverage transferable knowledge while adapting to the new task's specific requirements. 
Fine-tuning enables both the LSTM and fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
This is particularly beneficial when developing metamodels for complex VA contracts with limited simulation data. 
For instance, transferring information from GMMB contracts can still be valuable when modeling GMWB contracts.
Both contracts share some common contract features and temporal patterns, which allows a pre-trained LSTM metamodel to capture generalizable features that provide a solid foundation for the target task.

>>>>

\begin{table}[ht!]
    \centering
    \begin{tabular}{lrrr}
        \toprule
        \textbf{Model} & \textbf{Training Samples} & \textbf{Training MSE} & \textbf{True MSE} \\
        \midrule
        Without TL & 2,000 & 0.3588 & 0.4188 \\
        Fine Tuning & 2,000 & 0.1690 & 0.1780 \\
        Layer Freezing & 2,000 & 0.1828 & 0.2295 \\
        Extensive Training & 50,000 & 0.0853 & 0.0726 \\
        \bottomrule
    \end{tabular}
    \caption{Comparison of different TL methods to GMWB contracts}
    \label{tab3:transfer_learning_results_gmwb}
\end{table}

Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the LSTM metamodels on the GMWB contracts.
The TL methods are compared to training from scratch.
The suboptimal performance of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge significantly.
In such circumstances, fine-tuning provides a better approach by allowing the metamodel to leverage transferable knowledge while adapting to the new task's specific requirements. 
Fine-tuning enables both the LSTM and fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
This is particularly beneficial when developing metamodels for complex VA contracts with limited simulation data. 
For instance, transferring information from GMMB contracts can still be valuable when modeling GMWB contracts.
Both contracts share some common contract features and temporal patterns, which allows a pre-trained LSTM metamodel to capture generalizable features that provide a solid foundation for the target task.
